\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-12 Supplymentary.tex
Table 1 is formatted

\caption{\label{tab:MinResTab-31}Factor loadings and communality of the retained items(Minmum Residual)}

@@

\caption{\label{tab:sixFacTab-33}Factor loadings and communality of the retained items(six factor)}

@@

\caption{\label{tab:tabDesAppB-37}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-39-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB-39)
\end{figure}

@@

{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-43-1}

@@

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-43)
\end{figure}

@@

\caption{\label{tab:EFATableAppB-46}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-47-1}

@@

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-47)
\end{figure}
\end{appendix}

>>>>

\caption{\label{tab:MinResTab-33}Factor loadings and communality of the retained items(Minmum Residual)}

@@

\caption{\label{tab:sixFacTab-35}Factor loadings and communality of the retained items(six factor)}

@@

\caption{\label{tab:tabDesAppB-39}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-41-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB-41)
\end{figure}

@@

{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-45-1}

@@

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-45)
\end{figure}

@@

\caption{\label{tab:EFATableAppB-48}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-49-1}

@@

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-49)
\end{figure}
\end{appendix}
